Depression and suicidality as costly signals of need

### 2021-04-21 Paper.rmd
Added notes and one typo fix from my meeting with Anne Pisor.

Participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes. In the "basketball coach" scenario, the star player on a university basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by the coach. However, there are indications the player might be lying to get more playing time.

@@

>>>>

Participants in the US sample were randomly assigned to either the "basketball coach," "romantic partner," or "brother-in-law" vignettes. In the "basketball coach" scenario, the star player on a university basketball team comes to the participant (who is asked to imagine themselves as the athletic director at a university) and claims she was sexually assaulted by her coach. However, there are indications the player might be lying to get more playing time.

@@

# Notes from my meeting with Anne

- Table detailing the cooperative endeavor (maybe word as boundedness of fate), conflict of interest, and what the private information is about would be useful.
- Calling verbal request control when it's a treatment?
- Can shift much of the pilot studies info to SI with some detail post line 279 in draft she saw.
- Cumulative distribution plot: needs more info in captions. could benefit from fig6a and fig6b (confusion over x and y axes)
